### 2013-05-08 doc/icml2013/algo.tex
Expanded the whole of the whitening theorem

% Spectral
In recent years, there has a been substantial interest in ``spectral'' methods
for learning latent-variable models.  One line of work has
focused on observable operator models \cite{hsu09spectral}
in which the true parameters are not recovered, but a reparametrization is used
which enables prediction.
Another line of work is based on the method of moments and uses eigendecomposition of a certain tensor
to recover the parameters \cite{anandkumar12svd,anandkumar12moments,AnandkumarHsuKakade2012}.
Our work extends this line of work into the space of discriminative models,
which requires regression to obtain the desired tensor.

>>>>

% Spectral
In recent years, there has a been substantial interest in ``spectral'' methods
for learning latent-variable models.  One line of work has
focused on observable operator models \cite{hsu09spectral}
in which the true parameters are not recovered, but a reparametrization is used
which enables prediction.
Another line of work is based on the method of moments and uses eigendecomposition of a certain tensor
to recover the parameters \cite{anandkumar12lda,anandkumar12moments}.
Our work extends this line of work into the space of discriminative models,
which requires regression to obtain the desired tensor.

### 2013-05-08 doc/icml2013/intro.tex
Expanded the whole of the whitening theorem

% Recent method of moments spectral methods sidestep local optima
Recently, method of moments estimators have been developed for
\emph{generative} latent-variable models, including
mixture models, HMMs \cite{AnandkumarHsuKakade2012},
Latent Dirichlet Allocation \cite{anandkumar12lda},
and parsing models \cite{hsu12identifiability}.
The basic idea of this work is to express
the unknown model parameters as a tensor factorization
of the third-order moments of the model distribution, which
can be estimated from data.
The moments have a special symmetric structure
which permits the factorization to be computed efficiently using the robust
tensor power method \cite{AnandkumarGeHsu2012}.

@@

% Previous work: moment equations solvable by eigendecomposition or
% tensor factorization
%While method of moment estimators were \todo{described by Fisher(?)},
%they required as many moments as there were parameters, and hence deemed
%impractical. Recently, \citet{AnandkumarHsuKakade2012} showed how using
%eigendecomposition, the moment equations could be solved using just the
%first three moments of data.

>>>>

% Recent method of moments spectral methods sidestep local optima
Recently, method of moments estimators have been developed for
\emph{generative} latent-variable models, including
mixture models, HMMs \cite{anandkumar12moments},
Latent Dirichlet Allocation \cite{anandkumar12lda},
and parsing models \cite{hsu12identifiability}.
The basic idea of this work is to express
the unknown model parameters as a tensor factorization
of the third-order moments of the model distribution, which
can be estimated from data.
The moments have a special symmetric structure
which permits the factorization to be computed efficiently using the robust
tensor power method \cite{AnandkumarGeHsu2012}.

@@

% Previous work: moment equations solvable by eigendecomposition or
% tensor factorization
%While method of moment estimators were \todo{described by Fisher(?)},
%they required as many moments as there were parameters, and hence deemed
%impractical. Recently, \citet{anandkumar12moments} showed how using
%eigendecomposition, the moment equations could be solved using just the
%first three moments of data.
